---
title: "WAL Data Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r config-git}
usethis::use_git_config(user.name = "hanastepnick", user.email = "hana.stepnick@duke.edu")
```

```{r load}
library(tidyverse)
library(infer)
wal <- read_csv("wal.csv")
```

```{r majors}
majors <- wal %>%
  distinct(major)
```

Distribution of all major breakdowns:

```{r major-type-graph}
ggplot(data = wal, mapping = aes(x = major_type)) + 
  geom_bar()
```
Distribution of major breakdowns for females:

```{r majors-female}
wal_female <- wal %>%
  filter(gender == "Female")

ggplot(data = wal_female, mapping = aes(x = major_type)) + 
  geom_bar(fill = "purple")

```
Distribution of major breakdowns for males:

```{r majors-male}
wal_male <- wal %>%
  filter(gender == "Male")

ggplot(data = wal_male, mapping = aes(x = major_type)) + 
  geom_bar(fill = "blue")
```
Asking question:

```{r average-askquestion-f}
  mean(wal_female$ask_question, na.rm = FALSE)
```

```{r average-askquestion-m}
  mean(wal_male$ask_question, na.rm = FALSE)
```


```{r test-ask-question}
wal_male_female <- wal %>%
  filter(gender == "Female" | gender == "Male")
  
  
t_ask <- wal_male_female %>%
  t_test(ask_question ~ gender, 
         order = c("Female", "Male"), 
         alternative = "less", 
         conf_int = FALSE)
t_ask
```


Answering question:

```{r average-ansquestion-f}
  mean(wal_female$answer_question, na.rm = FALSE)
```

```{r average-ansquestion-m}
  mean(wal_male$answer_question, na.rm = FALSE)
```

```{r test-answer-question}
  
t_answer <- wal_male_female %>%
  t_test(answer_question ~ gender, 
         order = c("Female", "Male"), 
         alternative = "less", 
         conf_int = FALSE)
t_answer
```


Reach out to male prof:

```{r average-reachmale-f}
  mean(wal_female$reach_male, na.rm = FALSE)
```

```{r average-reachmale-m}
  mean(wal_male$reach_male, na.rm = FALSE)
```

```{r test-reach-male}
  
t_reach_male <- wal_male_female %>%
  t_test(reach_male ~ gender, 
         order = c("Female", "Male"), 
         alternative = "less", 
         conf_int = FALSE)
t_reach_male
```

Reach out to female prof:

```{r average-reachfemale-f}
  mean(wal_female$reach_female, na.rm = FALSE)
```

```{r average-reachfemale-m}
  mean(wal_male$reach_female, na.rm = FALSE)
```

```{r test-reach-female}
  
t_reach_female <- wal_male_female %>%
  t_test(reach_female ~ gender, 
         order = c("Male", "Female"), 
         alternative = "less", 
         conf_int = FALSE)
t_reach_female
```
Comfort with leading a group:

```{r average-lead-f}
  mean(wal_female$lead_group, na.rm = FALSE)
```

```{r average-lead-m}
  mean(wal_male$lead_group, na.rm = FALSE)
```

```{r test-lead}
  
t_lead <- wal_male_female %>%
  t_test(lead_group ~ gender, 
         order = c("Male", "Female"), 
         alternative = "less", 
         conf_int = FALSE)
t_lead
```


Comfort with disagreeing with group:

```{r average-disagree-f}
  mean(wal_female$disagree, na.rm = FALSE)
```

```{r average-disagree-m}
  mean(wal_male$disagree, na.rm = FALSE)
```

```{r test-disagree}
  
t_disagree <- wal_male_female %>%
  t_test(disagree ~ gender, 
         order = c("Male", "Female"), 
         alternative = "less", 
         conf_int = FALSE)
t_disagree
```

Comfort with keeping others accountable:

```{r average-accountable-f}
  mean(wal_female$accountable, na.rm = FALSE)
```

```{r average-accountable-m}
  mean(wal_male$accountable, na.rm = FALSE)
```

```{r test-grouplead}
t_accountable <- wal_male_female %>%
  t_test(accountable ~ gender, 
         order = c("Female", "Male"), 
         alternative = "less", 
         conf_int = FALSE)
t_accountable
```

Perceptions of major breakdowns:

```{r perception-stem}
wal_stem <- wal %>%
  filter(major_type == "Stem")

mean(wal_stem$breakdown, na.rm = FALSE)

```

```{r perception-humanities}
wal_humanities <- wal %>%
  filter(major_type == "Humanities")

mean(wal_humanities$breakdown, na.rm = FALSE)

```
```{r perception-socsci}
wal_social_science <- wal %>%
  filter(major_type == "Social Science")

mean(wal_social_science$breakdown, na.rm = FALSE)

```

```{r perception-engineering}
wal_engineering <- wal %>%
  filter(major_type == "Engineering")

mean(wal_engineering$breakdown, na.rm = FALSE)

```

```{r perception-engineering-and-stem}
wal_stem_engineering <- wal %>%
  filter(major_type == "Engineering" | major_type == "Stem")

mean(wal_stem_engineering$breakdown, na.rm = FALSE)

```


Engineering vs SS Gender Breakdown:
```{r engineering-ss}
wal_engineering_ss <- wal %>%
  filter(major_type == "Engineering" | major_type == "Social Science")

t_engineering_ss_breakdown <- wal_engineering_ss %>%
  t_test(breakdown ~ major_type, 
         order = c("Engineering", "Social Science"), 
         alternative = "less", 
         conf_int = FALSE)

t_engineering_ss_breakdown
```

Trinity vs. Pratt analyses:

Trinity: 

```{r trinity-female}
trinity_female <- wal %>%
  filter(school == "Trinity") %>%
  filter(gender == "Female")
```

```{r trinity-male}
trinity_male <- wal %>%
  filter(school == "Trinity") %>%
  filter(gender == "Male")
```

```{r female-ask-trinity}
mean(trinity_female$ask_question, na.rm = FALSE)
```

```{r male-ask-trinity}
mean(trinity_male$ask_question, na.rm = FALSE)
```

```{r trinity-ask}
wal_trinity <- wal %>%
  filter(school == "Trinity") %>%
  filter(gender == "Male" | gender == "Female")

t_ask_trinity <- wal_trinity %>%
  t_test(ask_question ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_ask_trinity
```


```{r female-answer-trinity}
mean(trinity_female$answer_question, na.rm = FALSE)
```

```{r male-answer-trinity}
mean(trinity_male$answer_question, na.rm = FALSE)
```


```{r trinity-answer}

t_answer_trinity <- wal_trinity %>%
  t_test(answer_question ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_answer_trinity
```

```{r female-reachmale-trinity}
mean(trinity_female$reach_male, na.rm = FALSE)
```

```{r male-reachmale-trinity}
mean(trinity_male$reach_male, na.rm = FALSE)
```


```{r trinity-reachmale}

t_reachmale_trinity <- wal_trinity %>%
  t_test(reach_male ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_reachmale_trinity
```

```{r female-reachfemale-trinity}
mean(trinity_female$reach_female, na.rm = FALSE)
```

```{r male-reachfemale-trinity}
mean(trinity_male$reach_female, na.rm = FALSE)
```


```{r trinity-reachfemale}

t_reachfemale_trinity <- wal_trinity %>%
  t_test(reach_female ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_reachfemale_trinity
```

```{r female-leadgroup-trinity}
mean(trinity_female$lead_group, na.rm = FALSE)
```

```{r male-leadgroup-trinity}
mean(trinity_male$lead_group, na.rm = FALSE)
```


```{r trinity-leadgroup}

t_leadgroup_trinity <- wal_trinity %>%
  t_test(lead_group ~ gender,
         order = c("Male", "Female"),  
         alternative = "less", 
         conf_int = FALSE)

t_leadgroup_trinity
```
```{r female-disagree-trinity}
mean(trinity_female$disagree, na.rm = FALSE)
```

```{r male-disagree-trinity}
mean(trinity_male$disagree, na.rm = FALSE)
```


```{r trinity-disagree}

t_disagree_trinity <- wal_trinity %>%
  t_test(disagree ~ gender,
         order = c("Male", "Female"),  
         alternative = "less", 
         conf_int = FALSE)

t_disagree_trinity
```

```{r female-accountable-trinity}
mean(trinity_female$accountable, na.rm = FALSE)
```

```{r male-accountable-trinity}
mean(trinity_male$accountable, na.rm = FALSE)
```


```{r trinity-accountable}

t_accountable_trinity <- wal_trinity %>%
  t_test(accountable ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_accountable_trinity
```


Pratt:

```{r pratt-female}
pratt_female <- wal %>%
  filter(school == "Pratt") %>%
  filter(gender == "Female")
```

```{r pratt-male}
pratt_male <- wal %>%
  filter(school == "Pratt") %>%
  filter(gender == "Male")
```

```{r female-ask-pratt}
mean(pratt_female$ask_question, na.rm = FALSE)
```

```{r male-ask-pratt}
mean(pratt_male$ask_question, na.rm = FALSE)
```

```{r pratt-ask}
wal_pratt <- wal %>%
  filter(school == "Pratt") %>%
  filter(gender == "Male" | gender == "Female")

t_ask_pratt <- wal_pratt %>%
  t_test(ask_question ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_ask_pratt
```


```{r female-answer-pratt}
mean(pratt_female$answer_question, na.rm = FALSE)
```

```{r male-answer-pratt}
mean(pratt_male$answer_question, na.rm = FALSE)
```


```{r pratt-answer}

t_answer_pratt <- wal_pratt %>%
  t_test(answer_question ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_answer_pratt
```

```{r female-reachmale-pratt}
mean(pratt_female$reach_male, na.rm = FALSE)
```

```{r male-reachmale-pratt}
mean(pratt_male$reach_male, na.rm = FALSE)
```


```{r pratt-reachmale}

t_reachmale_pratt <- wal_pratt %>%
  t_test(reach_male ~ gender,
         order = c("Male", "Female"),  
         alternative = "less", 
         conf_int = FALSE)

t_reachmale_pratt
```

```{r female-reachfemale-pratt}
mean(pratt_female$reach_female, na.rm = FALSE)
```

```{r male-reachfemale-pratt}
mean(pratt_male$reach_female, na.rm = FALSE)
```


```{r pratt-reachfemale}

t_reachfemale_pratt <- wal_pratt %>%
  t_test(reach_female ~ gender,
         order = c("Male", "Female"),  
         alternative = "less", 
         conf_int = FALSE)

t_reachfemale_pratt
```

```{r female-leadgroup-pratt}
mean(pratt_female$lead_group, na.rm = FALSE)
```

```{r male-leadgroup-pratt}
mean(pratt_male$lead_group, na.rm = FALSE)
```


```{r pratt-leadgroup}
t_leadgroup_pratt <- wal_pratt %>%
  t_test(lead_group ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_leadgroup_pratt
```

```{r female-disagree-pratt}
mean(pratt_female$disagree, na.rm = FALSE)
```

```{r male-disagree-pratt}
mean(pratt_male$disagree, na.rm = FALSE)
```


```{r pratt-disagree}

t_disagree_pratt <- wal_pratt %>%
  t_test(disagree ~ gender,
         order = c("Female", "Male"),  
         alternative = "less", 
         conf_int = FALSE)

t_disagree_pratt
```

```{r female-accountable-pratt}
mean(pratt_female$accountable, na.rm = FALSE)
```

```{r male-accountable-pratt}
mean(pratt_male$accountable, na.rm = FALSE)
```


```{r pratt-accountable}

t_accountable_pratt <- wal_pratt%>%
  t_test(accountable ~ gender,
         order = c("Male", "Female"),  
         alternative = "less", 
         conf_int = FALSE)

t_accountable_pratt
```